Effects of rarefaction

### 2021-04-13 analysis/reports/submission1/accessory/old_reports/synthesis.Rmd
reorganize branch

<!-- # Manipulations -->
<!-- # MACD -->

<!-- ```{r load macd, include =F} -->
<!-- cache_loc = "macdb" -->

<!-- ## Set up the cache and config -->
<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite"))) -->
<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->

<!-- all_di_macd <- readd(all_di_obs, cache = cache)  -->
<!-- all_di_macd_manip <- readd(all_di_manip, cache = cache) -->
<!-- macd_dat <- readd(dat_s_dat_macdb, cache = cache) -->

<!-- DBI::dbDisconnect(db) -->
<!-- rm(cache) -->

<!-- all_di_macd <- all_di_macd %>% -->
<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
<!--          log_nsamples = log(nsamples)) %>% -->
<!--   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
<!--   mutate(found_all = prop_found==1) -->
<!-- #  -->
<!-- # all_di_macd_manip <- all_di_macd_manip %>% -->
<!-- #   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
<!-- #          log_nsamples = log(nsamples)) %>% -->
<!-- #   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
<!-- #   mutate(found_all = prop_found==1) -->

<!-- ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw() -->

<!-- ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw() -->

<!-- ``` -->

<!-- Here are the distributions of skew and evenness, overall. -->

<!-- ```{r macd overall, include =F} -->

<!-- ggplot(data = all_di_macd, aes(x = skew_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->

<!-- ggplot(data = all_di_macd, aes(x = simpson_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->
<!-- ``` -->

<!-- Here is how manipulation affects things: -->

<!-- ```{r macd ctrlcomp, fig.dim = c(4,4), include =F} -->

<!-- ggplot(data = all_di_macd_manip, aes(x = skew_percentile, y = ctrl_skew_percentile)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   #  xlim(0, 100) + -->
<!--   # ylim(0, 100) + -->
<!--   theme_bw() + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->

<!-- ggplot(data = all_di_macd_manip, aes(x = simpson_percentile, y = ctrl_skew_percentile)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   xlim(0, 100) + -->
<!--   ylim(0, 100) + -->
<!--   theme_bw() + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->

<!-- ggplot(data = all_di_macd_manip, aes(x = simpson_change)) + -->
<!--   geom_histogram() + -->
<!--   theme_bw() -->

<!-- ggplot(data = all_di_macd_manip, aes(x = skew_change)) + -->
<!--   geom_histogram() + -->
<!--   theme_bw() -->

<!-- ggplot(data = all_di_macd_manip, aes(x = ctrl_simpson_percentile, y = simpson_change)) + -->
<!--   geom_point(alpha = .3) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   theme_bw() -->

<!-- ggplot(data = all_di_macd_manip, aes(x = ctrl_skew_percentile, y = skew_change)) + -->
<!--   geom_point(alpha = .3) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   theme_bw() -->

<!-- print(t.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T) -->
<!-- ) -->
<!-- print(t.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T) -->
<!-- ) -->

<!-- print(wilcox.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T)) -->
<!-- print(wilcox.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T)) -->

<!-- ``` -->

<!-- Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?) -->

<!-- # Portal plant manips -->

<!-- ```{r load pp, include = F} -->
<!-- cache_loc = "portal_plants_manip" -->

<!-- ## Set up the cache and config -->
<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite"))) -->
<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->

<!-- all_di_p<- readd(all_di_manip, cache = cache)  -->

<!-- all_di_p <- all_di_p %>% -->
<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
<!--          log_nsamples = log(nsamples)) %>% -->
<!--   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
<!--   mutate(found_all = prop_found==1) -->

<!-- DBI::dbDisconnect(db) -->
<!-- rm(cache) -->
<!-- ``` -->

<!-- Nsamples, singletons -->

<!-- ```{r pp overall, include = F} -->
<!-- #  -->
<!-- # ggplot(data = all_di_p, aes(x = nsamples)) + -->
<!-- #   geom_histogram(bins = 100) + -->
<!-- #   theme_bw() + -->
<!-- #   geom_vline(xintercept = 2000) -->
<!-- #  -->
<!-- # all_di_p <- filter(all_di_p, nsamples >= 2000) -->

<!-- ggplot(data = all_di_p, aes(x = skew_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->

<!-- ggplot(data = all_di_p, aes(x = simpson_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(found_all), scales = "free_y") -->
<!-- #  -->
<!-- # pp_singletons_effect <- all_di_p %>% -->
<!-- #   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>% -->
<!-- #   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile")) -->
<!-- #  -->
<!-- # ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) + -->
<!-- #   geom_point(alpha = .1) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!-- #   theme_bw() -->
<!-- #  -->
<!-- #  -->
<!-- # ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) + -->
<!-- #   geom_point(alpha = .1) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!-- #   theme_bw() -->
<!-- ``` -->

<!-- By treatment, season -->

<!-- ```{r portal trtmt, include =F} -->
<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season, treatment), scales = "free_y") -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season)) -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season, treatment), scales = "free_y") -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_wrap(vars(season)) -->
<!-- ``` -->

<!-- <!-- By year --> -->

<!-- <!-- ```{r plants year, fig.height = 25, fig.width = 5} --> -->

<!-- <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + --> -->
<!-- <!--   geom_boxplot() + --> -->
<!-- <!--   theme_bw() + --> -->
<!-- <!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") --> -->
<!-- <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + --> -->
<!-- <!--   geom_boxplot() + --> -->
<!-- <!--   theme_bw() + --> -->
<!-- <!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") --> -->
<!-- <!-- ``` --> -->

<!-- Median -->
<!-- ```{r pp median, fig.width = 12, fig.height = 12, include =F} -->

<!-- pp_median <- all_di_p %>% -->
<!--   filter(singletons == F) %>% -->
<!--   group_by(season, year, treatment) %>% -->
<!--   summarize(skew_percentile = median(skew_percentile), -->
<!--             simpson_percentile = median(simpson_percentile)) %>% -->
<!--   ungroup() %>% -->
<!--   tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile)) -->

<!-- sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Skew Ctrl v Exclosure") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(40, 100) + -->
<!--   ylim(40, 100) -->

<!-- sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Skew Ctrl v Removal") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(40, 100) + -->
<!--   ylim(40, 100) -->

<!-- gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2) -->

<!-- sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Simpson Ctrl v Exclosure") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(0, 40) + -->
<!--   ylim(0, 40) -->

<!-- sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) + -->
<!--   geom_point(alpha = .5) + -->
<!--   facet_wrap(vars(season)) + -->
<!--   theme_bw() + -->
<!--   ggtitle("Simpson Ctrl v Removal") + -->
<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
<!--   xlim(0, 40) + -->
<!--   ylim(0, 40) -->

<!-- gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2) -->
<!-- ``` -->

```{r nparts v rov}

all_di_plot <- filter(all_di, !singletons)

ggplot(all_di_plot, aes(x = log_nparts, y = simpson_mean)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(all_di_plot, aes(x = log_nparts, y = simpson_sd)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(all_di_plot, aes(x = log_nparts, y = abs(simpson_sd/simpson_mean))) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(all_di_plot, aes(x = abs(simpson_sd/simpson_mean), y = simpson_percentile, color = log_nparts > 10)) +
  geom_point(alpha = .05) +
  theme_bw() +
  scale_color_viridis_d(end = .8)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = skew_mean)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = skew_sd)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = abs(skew_sd/skew_mean))) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_vline(xintercept = 10)

ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = abs(skew_sd/skew_mean), y = skew_percentile, color = log_nparts > 10)) +
  geom_point(alpha = .05) +
  theme_bw() +
  scale_color_viridis_d(end = .8) +
  xlim(0,4)
```

>>>>

# Manipulations
# MACD

```{r load macd}
cache_loc = "macdb"

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

all_di_macd <- readd(all_di_obs, cache = cache) 
all_di_macd_manip <- readd(all_di_manip, cache = cache)
macd_dat <- readd(dat_s_dat_macdb, cache = cache)

DBI::dbDisconnect(db)
rm(cache)

all_di_macd <- all_di_macd %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1)
# 
# all_di_macd_manip <- all_di_macd_manip %>%
#   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
#          log_nsamples = log(nsamples)) %>%
#   mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
#   mutate(found_all = prop_found==1)

ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()

ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()

Here are the distributions of skew and evenness, overall.

```{r macd overall}

ggplot(data = all_di_macd, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")

ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")
```

Here is how manipulation affects things:

```{r macd ctrlcomp, fig.dim = c(4,4)}

ggplot(data = all_di_macd_manip, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
  geom_point(alpha = .5) +
  #  xlim(0, 100) +
  # ylim(0, 100) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = all_di_macd_manip, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
  geom_point(alpha = .5) +
  xlim(0, 100) +
  ylim(0, 100) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = all_di_macd_manip, aes(x = simpson_change)) +
  geom_histogram() +
  theme_bw()

ggplot(data = all_di_macd_manip, aes(x = skew_change)) +
  geom_histogram() +
  theme_bw()

ggplot(data = all_di_macd_manip, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
  geom_point(alpha = .3) +
  geom_hline(yintercept = 0) +
  theme_bw()

ggplot(data = all_di_macd_manip, aes(x = ctrl_skew_percentile, y = skew_change)) +
  geom_point(alpha = .3) +
  geom_hline(yintercept = 0) +
  theme_bw()

print(t.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T)
)
print(t.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T)
)

print(wilcox.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T))
print(wilcox.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T))

Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?)

# Portal plant manips

```{r load pp}
cache_loc = "portal_plants_manip"

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

all_di_p<- readd(all_di_manip, cache = cache)

all_di_p <- all_di_p %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1)

DBI::dbDisconnect(db)
rm(cache)
```

Nsamples, singletons

```{r pp overall}
# 
# ggplot(data = all_di_p, aes(x = nsamples)) +
#   geom_histogram(bins = 100) +
#   theme_bw() +
#   geom_vline(xintercept = 2000)
# 
# all_di_p <- filter(all_di_p, nsamples >= 2000)

ggplot(data = all_di_p, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")

ggplot(data = all_di_p, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(found_all), scales = "free_y")
# 
# pp_singletons_effect <- all_di_p %>%
#   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
#   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
# 
# ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
#   geom_point(alpha = .1) +
#   geom_abline(intercept = 0, slope = 1, color = "green") +
#   theme_bw()
# 
# 
# ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
#   geom_point(alpha = .1) +
#   geom_abline(intercept = 0, slope = 1, color = "green") +
#   theme_bw()
```

By treatment, season

```{r portal trtmt}
ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(season, treatment), scales = "free_y")

ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap(vars(season))

ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(season, treatment), scales = "free_y")

ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
  geom_boxplot() +
  theme_bw() +
  facet_wrap(vars(season))
```

<!-- By year -->

<!-- ```{r plants year, fig.height = 25, fig.width = 5} -->

<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + -->
<!--   geom_boxplot() + -->
<!--   theme_bw() + -->
<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
<!-- ``` -->

Median
```{r pp median, fig.width = 12, fig.height = 12}

pp_median <- all_di_p %>%
  filter(singletons == F) %>%
  group_by(season, year, treatment) %>%
  summarize(skew_percentile = median(skew_percentile),
            simpson_percentile = median(simpson_percentile)) %>%
  ungroup() %>%
  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))

sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Skew Ctrl v Exclosure") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(40, 100) +
  ylim(40, 100)

sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Skew Ctrl v Removal") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(40, 100) +
  ylim(40, 100)

gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)

sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Simpson Ctrl v Exclosure") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(0, 40) +
  ylim(0, 40)

sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
  geom_point(alpha = .5) +
  facet_wrap(vars(season)) +
  theme_bw() +
  ggtitle("Simpson Ctrl v Removal") +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  xlim(0, 40) +
  ylim(0, 40)

gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
```

### 2021-04-13 analysis/reports/submission1/accessory/rarefaction.Rmd
reorganize branch

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))
```

@@

adjusted_comparison <- all_di %>%
  select(dat, site, singletons, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile_excl, nsingletons_percentile, mean_po_comparison_percentile, log_nparts) %>%
  tidyr::pivot_wider(id_cols = c(dat, site), names_from = singletons, values_from = c(s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile_excl, nsingletons_percentile, mean_po_comparison_percentile, log_nparts))

overall_results <- adjusted_comparison %>%
  filter(s0_FALSE > 2, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)) %>%
  mutate(high_skew_raw = skew_percentile_excl_FALSE > 95,
         high_skew_adjusted = skew_percentile_excl_TRUE > 95,
         low_even_raw = simpson_percentile_FALSE < 5,
         low_even_adjusted = simpson_percentile_TRUE < 5,
         low_shannon_raw = shannon_percentile_FALSE <5,
         low_shannon_adjusted = shannon_percentile_TRUE < 5,
         high_singletons_raw = nsingletons_percentile_excl_FALSE > 95,
         high_singletons_adjusted = nsingletons_percentile_excl_TRUE > 95,
         low_singletons_raw = nsingletons_percentile_FALSE < 5,
         low_singletons_adjusted = nsingletons_percentile_TRUE < 5,
         high_po_raw = mean_po_comparison_percentile_FALSE > 95,
         high_po_adjusted = mean_po_comparison_percentile_TRUE > 95)

summary_vars <- colnames(overall_results)[ c(which(grepl("raw", colnames(overall_results))), which(grepl("adjusted", colnames(overall_results))))]

overall_results <- overall_results %>%
  group_by(dat) %>%
  summarize_at(summary_vars, mean)

# overall_simpson_results <- adjusted_comparison %>%
#    filter(log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)) %>%
#   mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
#          low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
#   group_by(dat) %>%
#   summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
#             proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
#             nsites_simpson = dplyr::n())
# 
# overall_results <- left_join(overall_skew_results, overall_simpson_results)

overall_results

ggplot(filter(adjusted_comparison, s0_FALSE > 2, log_nparts_TRUE > log(20), log_nparts_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, s0_FALSE > 2, log_nparts_TRUE > 20, log_nparts_FALSE > log(20)), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(shannon_percentile_FALSE, shannon_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(shannon_percentile_FALSE, shannon_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(nsingletons_percentile_excl_FALSE, nsingletons_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(nsingletons_percentile_excl_FALSE, nsingletons_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

>>>>

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         s0 > 1,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
```

@@

adjusted_comparison <- all_di %>%
  select(dat, site, singletons, s0, n0, skew_percentile_excl, simpson_percentile, log_nparts, simpson_unique, skew_unique) %>%
  tidyr::pivot_wider(id_cols = c(dat, site), names_from = singletons, values_from = c(s0, n0, skew_percentile_excl, simpson_percentile, log_nparts, simpson_unique, skew_unique))

overall_skew_results <- adjusted_comparison %>%
  filter(s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20) %>%
  mutate(high_skew_raw = skew_percentile_excl_FALSE > 95,
         high_skew_adjusted = skew_percentile_excl_TRUE > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high_raw = mean(high_skew_raw),
            proportion_skew_high_adjusted = mean(high_skew_adjusted),
            nsites_skew = dplyr::n())

overall_simpson_results <- adjusted_comparison %>%
   filter(simpson_unique_TRUE > 20, simpson_unique_FALSE > 20) %>%
  mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
         low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
  group_by(dat) %>%
  summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
            proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
            nsites_simpson = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results)

ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

overall_skew_results

ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat)) 
overall_simpson_results
```
